\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://binacs.cn/}{\Large Bing Li}}\\
  \href{https://binacs.cn}{https://binacs.cn}
  & Email : \href{mailto:bin646891055@gmail.com}{bin646891055@gmail.com}\\
  \href{https://github.com/binacslee}{https://github.com/binacslee}
  & Mobile : +086-132-7706-5357 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{http://cse.whu.edu.cn}{School of Cyber Science and Engineering},
      \href{https://en.whu.edu.cn}{Wuhan University}}{Wuhan, CN}
      {Bachelor of Engineering in Information Security;  GPA: 3.27 / 4.00}{Sep. 2015 -- Jun. 2019}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Go / C++}
    \resumeSubItem{Technologies}{Kubernetes / Docker / Redis}
    \resumeSubItem{Distributed Consensus}{PBFT / RAFT}
    \resumeSubItem{Competitive Programming}{\href{https://leetcode-cn.com/u/binacslee-cn/}{LeetCode Contest rating 2300+}}
  \resumeSubHeadingListEnd
  
%-----------OPEN SOURCE CONTRIBUTION-----------------
\section{Open Source Contribution}
  \resumeSubHeadingListStart
    \resumeSubItem{Especially familiar with}
    {\textbf{}{Kubernetes scheduling / Ethereum architecture.}}
    \resumeSubItem{Member of}
    {\textbf{}{
      \href{https://github.com/kubernetes}{Kubernetes} /
      \href{https://github.com/kubernetes-sigs}{Kubernetes SIGs} /
      \href{https://github.com/istio}{Istio}.}}
    \resumeSubItem{Contributor of}
    {\textbf{}{
      \href{https://github.com/ethereum}{ethereum} /
      \href{https://github.com/etcd-io}{etcd-io} etc.}}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Xunlei Ltd}{Shenzhen, CN}
      {Blockchain Protocol Engineer}{Jul 2019 - Present}
      \resumeItemListStart
        \resumeItem{ThunderChain}
          {ThunderChain is a high-performance blockchain that supports plug-in consensus.
          Refactored the consensus module and participated in the self-developed higher-performance
          BALAS consensus; rewritten the relay node to reduce the performance consumption by 80\%,
          and the transaction forwarding performance was 1.7 times the original.}
        \resumeItem{BaaS}
          {Blockchain as a Service provides a platform for the public to build a
          complete blockchain ecosystem easily.
          Responsible for designing and implementing a BaaS solution based on kubernetes, which solved the 
          problems of blockchain adaptation, node persistent storage, node scheduling and dynamic migration; 
          wrote a new Dockerfile to support CGO, reducing the original container size by 90\%}
        \resumeItem{TC Monitor}
          {TC Monitor is a service that collects and displays ThunderChain monitoring. Participated in
          the design of the implementation of low-code intrusion monitoring, independently wrote the
          ThunderChain exporter and supported prometheus and opentracing at the blockchain layer.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/BinacsLee/server}{server}}
      {Runs on Kubernetes and powers \href{https://binacs.cn/}{binacs.cn}.
      Support   \href{https://binacs.cn/toys/crypto}{Crypto} / 
                \href{https://binacs.cn/toys/pastebin}{Pastebin} / 
                \href{https://binacs.cn/toys/tinyurl}{TinyURL} / 
                \href{https://binacs.cn/toys/storage}{Storage}
      etc.}
    \resumeSubItem{\href{https://github.com/BinacsLee/cli}{cli}}
      {Terminal client for \href{https://github.com/BinacsLee/server}{server}. Quick visit
      \href{https://binacs.cn/}{binacs.cn}. Use gRPC protocol for communication.}
    \resumeSubItem{\href{https://github.com/binacsgo/inject}{inject}}
      {Dependency injection library for Go.}
    % \resumeSubItem{\href{https://github.com/binacsgo/pqueue}{pqueue}}
    %   {PQueue written in Go, based on LRU algorithm.}
    % \resumeSubItem{\href{https://github.com/OpenKikCoc/deployment-cpeditor-ide}{deployment-cpeditor-ide}}
    %   {Docker deployment for CP Editor IDE. Support GUI with noVNC.}
    \resumeSubItem{More at}
      {\href{https://github.com/BinacsLee}{BinacsLee} /
       \href{https://github.com/OpenKikCoc}{OpenKikCoc} /
       \href{https://github.com/binacsgo}{binacsgo}.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}